### 2016-05-02 text/abstraction_relation.tex
Add reviewer's comments into the paper.

We begin by defining which transformation executions an empty path condition
will abstract. \cref{fig:empty_pc} demonstrates two cases. In each, the path
condition is on the left-hand side, and a transformation execution is on the
right-hand side. Note that in \cref{fig:empty_pc_success}, the path condition
abstracts the transformation execution, while in \cref{fig:empty_pc_fail}, the
abstraction relation does not hold.

@@

The first condition for the abstraction relation is to determine whether a typed graph injective homomorphism can be found between the match graph of the path condition, and an transformation executions. Note that in both \cref{fig:empty_pc_success} and \cref{fig:empty_pc_fail}, an empty typed graph homomorphism satisfies this condition, highlighted by blue arrows.

@@

\begin{itemize}
  \item \emph{Base case:} the base case is when $tr$ is the empty
  transformation. In this case, according to \cref{def:path_cond_gen} only the
  empty path condition $\epsilon_{pc}$ exists in the path condition set. We thus
  need to demonstrate that the empty path condition abstracts the empty
  transformation execution $\epsilon_{ex}$, as well as any execution for which
  the input model is never matched by any rule (consequently having an empty
  output model). For any of these transformation executions, Proposition~\ref{eq:abstr_input_output} of the abstraction relation definition is satisfied, as no rule copy exists in the path condition and the output of the transformation execution is empty -- empty typed graph homomorphisms thus satisfy the all the conditions of the proposition. Proposition~\ref{eq:abstr_trace} of the abstraction relation definition also trivially holds because no traceability links exist either in the path condition or in any of the considered executions.

@@

  \item \emph{Inductive case:} for the inductive case (transitive case of \cref{def:path_cond_layer_comb}) we need to show that, assuming the property holds for all path conditions generated for a transformation $tr$, then the property will also hold for a transformation $tr'$ -- where $tr'$ results from adding a new rule $rl$ to the last layer of $tr$. We will thus need to consider the four cases of rule combination:\vspace{.2cm}

@@

We will do so by attempting to to build an $ex\in \textsc{Exec}(tr)$ such that $ex\Vvdash pc_1$ and $ex\Vvdash pc_2$ and demonstrating that it is always the case that such is not possible. In order to structure our argumentation, we will consider two cases:
% \levi{the contradiction happens because at each point of the execution, when a rule is added any two path conditions from the existing set of path conditions will represent different executions. At all points if we consider two path conditions in the PC set we have that two different executions can be created if we find a model that satisfies the first condition of the abstraction relation, and it is always the case that none of those two executions can be abstracted by the two path conditions simultaneously.}
\begin{enumerate}
  \item\label{item:uniqueness_rule_no_dep} the case where no rules in $tr$ have dependencies.
  \item\label{item:uniqueness_rule_has_dep} the case where some rules in $tr$ have dependencies.
\end{enumerate}

>>>>

We begin by defining which transformation executions an empty path condition
will abstract. \cref{fig:empty_pc} demonstrates two cases. In each, the path
condition \textit{pc} is on the left-hand side, and a transformation execution \textit{ex} is on the
right-hand side. Note that in \cref{fig:empty_pc_success}, the path condition
abstracts the transformation execution, while in \cref{fig:empty_pc_fail}, the
abstraction relation does not hold.

@@

The first condition for the abstraction relation is to determine whether a typed graph injective homomorphism can be found between the match graph of the path condition, and a transformation execution. Note that in both \cref{fig:empty_pc_success} and \cref{fig:empty_pc_fail}, an empty typed graph homomorphism satisfies this condition, highlighted by blue arrows.

@@

\begin{itemize}
  \item \emph{Base case:} the base case is when $tr$ is the empty
  transformation. In this case, according to \cref{def:path_cond_gen} only the
  empty path condition $\epsilon_{pc}$ exists in the path condition set. We thus
  need to demonstrate that the empty path condition abstracts the empty
  transformation execution $\epsilon_{ex}$, as well as any execution for which
  the input model is never matched by any rule (consequently having an empty
  output model). For any of these transformation executions, Proposition~\ref{eq:abstr_input_output} of the abstraction relation definition is satisfied, as no rule copy exists in the path condition and the output of the transformation execution is empty -- empty typed graph homomorphisms thus satisfy all the conditions of the proposition. Proposition~\ref{eq:abstr_trace} of the abstraction relation definition also trivially holds because no traceability links exist either in the path condition or in any of the considered executions.

@@

  \item \emph{Inductive case:} for the inductive case (transitive case of \cref{def:path_cond_layer_comb}) we need to show that, assuming the property holds for all path conditions generated for a transformation $tr$, then the property will also hold for a transformation $tr'$ -- where $tr'$ results from adding a new rule $rl$ to the last layer of $tr$. We will thus need to consider the four \reviewer{three?} cases of rule combination:\vspace{.2cm}

@@

We will do so by attempting to build an $ex\in \textsc{Exec}(tr)$ such that $ex\Vvdash pc_1$ and $ex\Vvdash pc_2$ and demonstrating that it is always the case that such is not possible. In order to structure our argumentation, we will consider two cases:
% \levi{the contradiction happens because at each point of the execution, when a rule is added any two path conditions from the existing set of path conditions will represent different executions. At all points if we consider two path conditions in the PC set we have that two different executions can be created if we find a model that satisfies the first condition of the abstraction relation, and it is always the case that none of those two executions can be abstracted by the two path conditions simultaneously.}
\begin{enumerate}
  \item\label{item:uniqueness_rule_no_dep} the case where no rules in $tr$ have dependencies.
  \item\label{item:uniqueness_rule_has_dep} the case where some rules in $tr$ have dependencies.
\end{enumerate}

### 2016-05-02 text/appendix_property_proof.tex
Add reviewer's comments into the paper.

\begin{proposition}{(Completeness) Properties of a transformation can be shown to either hold for all transformation executions, or not hold for at least one transformation execution.}
\label{prop:proof_completeness_appendix}
\end{proposition}
\begin{proof}
This results follows from two previous results: \cref{prop:pc_completeness_appendix}, that tells us that every transformation execution is abstracted by one path condition; and \cref{prop:proof_validity_appendix} that shows us that every path condition is taken into consideration during property proof. Note that \cref{lem:uniqueness_appendix} guarantees consistency of our results, in the sense that the uniqueness of one path condition per transformation execution guarantees that a property cannot be proven to be both \emph{true} and \emph{false} for two path conditions representing the same transformation execution.
\end{proof}

>>>>

\begin{proposition}{(Completeness) Properties of a transformation can be shown to either hold for all transformation executions, or not hold for at least one transformation execution.}
\label{prop:proof_completeness_appendix}
\end{proposition}
\begin{proof}
This result follows from two previous results: \cref{prop:pc_completeness_appendix}, that tells us that every transformation execution is abstracted by one path condition; and \cref{prop:proof_validity_appendix} that shows us that every path condition is taken into consideration during property proof. Note that \cref{lem:uniqueness_appendix} guarantees consistency of our results, in the sense that the uniqueness of one path condition per transformation execution guarantees that a property cannot be proven to be both \emph{true} and \emph{false} for two path conditions representing the same transformation execution.
\end{proof}

### 2016-05-02 text/building_path_conditions.tex
Add reviewer's comments into the paper.

According to the pre-conditions of the equation presented in \cref{def:rule_comb_unsatisfied}, a path condition does not satisfy the dependencies present in a rule if there is no surjective typed graph homomorphism between the backward links of the rule and the symbolic traceability links of the path condition. Besides expressing the fact that all backward links must exist as symbolic traceability links the path condition, the surjective homomorphism allows modeling the case where dependencies expressed by two (or more) backward links between similarly typed elements can be satisfied one single symbolic traceability link in the path condition. This is the case, for example, of rule \emph{FemaleToFemale} in the \emph{Police Station} in \cref{fig:dsltransformation}. The two similarly typed backward links in this rule are satisfied by a path condition containing only the rule \emph{females} generated from the first layer of the transformation, holding one single symbolic traceability link.

@@

\begin{figure*}[htb]
        \centering
        \begin{subfigure}[b]{0.7\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/total_satisfied_dependencies.pdf}
                \caption{Totally satisfied at one location}
                \label{fig:total_satisfied_dependencies}
        \end{subfigure}%
        \\
        \begin{subfigure}[b]{0.8\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/multiple_total_satisfied_dependencies.pdf}
                \caption{Totally satisfied at multiple locations}
                \label{fig:multiple_total_satisfied_dependencies}
        \end{subfigure}%
        \caption{R's dependencies are totally satisfied by PC}
        \label{fig:totes_sat_deps}
\end{figure*}

>>>>

According to the pre-conditions of the equation presented in \cref{def:rule_comb_unsatisfied}, a path condition does not satisfy the dependencies present in a rule if there is no surjective typed graph homomorphism between the backward links of the rule and the symbolic traceability links of the path condition. Besides expressing the fact that all backward links must exist as symbolic traceability links the path condition, the surjective homomorphism allows modeling the case where dependencies expressed by two (or more) backward links between similarly typed elements can be satisfied by one single symbolic traceability link in the path condition \reviewer{Could be rephrased}. This is the case, for example, of rule \emph{FemaleToFemale} in the \emph{Police Station} in \cref{fig:dsltransformation}. The two similarly typed backward links in this rule are satisfied by a path condition containing only the rule \emph{females} generated from the first layer of the transformation, holding one single symbolic traceability link.

@@

\begin{figure*}[htb]
        \centering
        \begin{subfigure}[b]{0.7\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/total_satisfied_dependencies.pdf}
                \caption{Totally satisfied at one location}
                \label{fig:total_satisfied_dependencies}
        \end{subfigure}%
        \\
        \begin{subfigure}[b]{0.8\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/building_path_conditions/multiple_total_satisfied_dependencies.pdf}
                \caption{Totally satisfied at multiple locations - \reviewer{Fix boxes on bottom}}
                \label{fig:multiple_total_satisfied_dependencies}
        \end{subfigure}%
        \caption{R's dependencies are totally satisfied by PC}
        \label{fig:totes_sat_deps}
\end{figure*}

### 2016-05-02 text/definitions.tex
Add reviewer's comments into the paper.

%<*typedgraphtext>

We will start by introducing the notion of typed graph. A typed graph is the essential object we will use throughout our mathematical development. Typed graphs will be used to formalise all the important graph-like structures we will present in this paper. A typed graph is a directed multigraph (a graph allowing multiple edges between two vertices) where vertices and edges are typed.

@@

%<*typedgraphhomomorphismtext>

For the formal development of our technique, we are interested in relations between typed graphs that are structure-preserving, i.e. homomorphisms. Homomorphisms between typed graphs preserve not only structure, but also the types of vertices and edges that are mapped.

@@

Let $rl = \big\langle V,E,st,\tau, Match,Apply\big\rangle$ be a transformation rule where $Match =\langle V_m, E_m, st_m, \tau_m\rangle$. We define $rl$'s matcher, noted $\Vert rl\Vert$, as the transformation rule $\big\langle V',E',st',\tau',Match,\\Apply'\big\rangle\sqsubseteq rl$ where $v_1\xrightarrow{e} v_2\in E'$ if and only if $v_1,v_2\in Match$ or $\tau(e)=trace$ and $V'=V_m\cup \big\{v_1\,|\,v_1\xrightarrow{e} v_2\in E \land \tau(e)=trace\big\}$.

%</backmatchtransformationrule>

@@

%'transformation rule cref in text
introduces the notion of matcher for a transformation rule which consists solely of the match pattern of a rule and its backward links, if any. The matcher of a rule constitutes the complete pattern that a DSLTrans rule attempts to match over a input-output model during rule execution. Traceability links between input and output model elements generated during transformation execution are matched by transformation rules' backward links, as informally explained in \cref{subsec:DSLTrans_constructs}.

@@

%<*layertransformationtext>

\cref{def:layer_transformation} formalises the abstract syntax of a model transformation, introduced in \cref{sec:dsltrans}. An example of a model transformation can be observed in \cref{fig:dsltransformation}, the Police Station transformation. As expected, a formal DSLTrans transformation is composed of a sequence of layers where each layer is composed of a set of rules. The last condition of \cref{def:layer_transformation} imposes that, for any two pair of rules in the transformation, the matcher of the second rule never partially or totally subsumes (or contains) the matcher of the first rule, unless the second rule is in a subsequent layer and produces something more than the first rule. This condition avoids situations where the execution of a rule in a DSLTrans model transformation necessarily implies the execution of another rule (except for when rules having backward links necessarily execute because all their dependencies were created during the execution of previous layers).

@@

%<*layertransformationtextappendix>

\cref{def:layer_transformation_appendix} formalises the abstract syntax of a model transformation, introduced at the beginning of this section. An example of a model transformation can be observed in \cref{fig:dsltransformation}, the Police Station transformation. As expected, a formal DSLTrans transformation is composed of a sequence of layers where each layer is composed of a set of rules. The last condition of \cref{def:layer_transformation_appendix} imposes that, for any two pair of rules in the transformation, the matcher of the second rule never partially or totally subsumes (or contains) the matcher of the first rule, unless the second rule is in a subsequent layer and produces something more than the first rule. This condition avoids situations where the execution of a rule in a DSLTrans model transformation necessarily implies the execution of another rule (except for when rules having backward links necessarily execute because all their dependencies were created during the execution of previous layers).

@@

%<*pccfrc>

@@

where we have that $V=V'\cup V''$, $E'\cup E''\subseteq E$, $st'\cup
st''\subseteq st$, $\tau'\cup \tau''\subseteq \tau$ and if $v_1\xrightarrow{e}
v_2\in E\setminus E'\cup E''$ then we have that $v_1\in Apply(V'')$, $v_1\notin Apply(V')$, $v_2\in Match(V'')$ and also that $\tau'(e)=trace$. Additionally, $Match = Match'\sqcup Match''$ and $Apply = Apply'\sqcup Apply''$. Finally, we have that: $Rulecop = Rulecop'\cup rl$.

@@

Let $tr\in \textsc{Transf}^{sr}_{tg}$ be a DSLTrans transformation. Let also $pc = \langle V,E,st,\tau,Match,Apply,Rules\rangle \in
\textsc{Pathcond}(tr)$ of be a path condition of $tr$ and $ex = \langle V',E',st',\tau',Input,Output\rangle \in Exec(tr)$ be an execution of $tr$. We have that $ex$ is abstracted by $pc$, noted $ex\Vvdash pc$, if and only if the set of transformation rules of $tr$ combined in $pc$ and the set of transformation rules of $tr$ used to built $ex$ is the same, and:
\begin{multline}
\label{eq:abstr_input_output}
\big(\forall rl\in Rules\;.\;Match(rl) \vartriangleleft Input^*\big) \;\land\; Output \blacktriangleleft Apply
\end{multline}
\center{and}
\begin{multline}
\label{eq:abstr_trace}
\big(\forall trc\in Components(pc|_{trace})\;.\;trc\vartriangleleft ex\big)\;\land\;\\
\big(\forall e'\in E'\, \exists e\in E\;.\;\tau'(e')=trace \Longrightarrow \tau(e)=trace\big)
\end{multline} 
% where for all $rl,rl'\in Rules$, if $rl\cong rl'$ then there exist two injective typed graph homomorphisms $f$ and $g$ such that $Match(rl)\stackrel{f}{\vartriangleleft} Input^*$, $Match(rl)\stackrel{g}{\vartriangleleft} Input^*$ and $CoDom(f)\neq CoDom(g)$.
% $/pc/ = Apply_{ex}\cup ex|_{trace}$ is the output part of $pc$, including symbolic traceability links.

%</abstractionrel>

@@

@@

Let $tr\in \textsc{Transf}^{sr}_{tg}$ be a transformation. Let also $p = \langle V,E,st,\tau,\\Pre,Post\rangle \in \textsc{Property}(tr)$ be a property of $tr$ and $pc=\big\langle V',E',\\st',\tau', Match,Apply,Rulecop\big\rangle\in \textsc{Pathcond}(tr)$ be a path condition of $tr$. Path condition $pc$ satisfies property $p$, written $pc \vdash p$, if and only if:
\begin{multline*}
\forall f\; \exists g\,.\,\big(in\stackrel{f}{\blacktriangleleft} Pre \implies out \stackrel{g}\blacktriangleleft p\big)\\
\text{where } in \sqsubseteq Match^{*} \;\land\; out \sqsubseteq pc^{*}
\end{multline*}
Additionally $Dom(g)\cap Match(pc^{*}) = Dom(f)$ and $f(v)\neq f(v')$, $g(v)\neq g(v')$ whenever $v$ and $v'$ are elements of the path condition belonging to the same rule copy of set $Rulecop$.

>>>>

%<*typedgraphtext>
We will start by introducing the notion of typed graph. A typed graph is the essential object we will use throughout our mathematical development. Typed graphs will be used to formalise all the important graph-like structures we will present in this paper. A typed graph is a directed multigraph (a graph allowing multiple edges between two vertices) where vertices and edges are typed.

@@

%<*typedgraphhomomorphismtext>
\reviewer{definition 3:''st'' was before ''(s, t)'' in the previous definitions (idem with ''stâ''), in the same way in definition 13, both notations are used.}
For the formal development of our technique, we are interested in relations between typed graphs that are structure-preserving, i.e. homomorphisms. Homomorphisms between typed graphs preserve not only structure, but also the types of vertices and edges that are mapped.

@@

Let $rl = \big\langle V,E,st,\tau, Match,Apply\big\rangle$ be a transformation rule where $Match =\langle V_m, E_m, st_m, \tau_m\rangle$. We define $rl$'s matcher, noted $\Vert rl\Vert$, as the transformation rule $\big\langle V',E',st',\tau',Match,\\Apply'\big\rangle\sqsubseteq rl$ where $v_1\xrightarrow{e} v_2\in E'$ if and only if $v_1,v_2\in Match$ or $\tau(e)=trace$ and $V'=V_m\cup \big\{v_1\,|\,v_1\xrightarrow{e} v_2\in E \land \tau(e)=trace\big\}$.
\reviewer{Definition 14: where does Apply' come from? Should v1 be 
  an element of Apply?}
%</backmatchtransformationrule>

@@

%'transformation rule cref in text

introduces the notion of matcher for a transformation rule which consists solely of the match pattern of a rule and its backward links, if any. The matcher of a rule constitutes the complete pattern that a DSLTrans rule attempts to match over a input-output model during rule execution. Traceability links between input and output model elements generated during transformation execution are matched by transformation rules' backward links, as informally explained in \cref{subsec:DSLTrans_constructs}.

@@

%<*layertransformationtext>
\reviewer{I do not fully understand why this
  could be problematic. Do you have an example?}
\cref{def:layer_transformation} formalises the abstract syntax of a model transformation, introduced in \cref{sec:dsltrans}. An example of a model transformation can be observed in \cref{fig:dsltransformation}, the Police Station transformation. As expected, a formal DSLTrans transformation is composed of a sequence of layers where each layer is composed of a set of rules. The last condition of \cref{def:layer_transformation} imposes that, for any two pair of rules in the transformation, the matcher of the second rule never partially or totally subsumes (or contains) the matcher of the first rule, unless the second rule is in a subsequent layer and produces something more than the first rule. This condition avoids situations where the execution of a rule in a DSLTrans model transformation necessarily implies the execution of another rule (except for when rules having backward links necessarily execute because all their dependencies were created during the execution of previous layers).

@@

%<*layertransformationtextappendix>
\reviewer{I do not fully understand why this
  could be problematic. Do you have an example?}
\cref{def:layer_transformation_appendix} formalises the abstract syntax of a model transformation, introduced at the beginning of this section. An example of a model transformation can be observed in \cref{fig:dsltransformation}, the Police Station transformation. As expected, a formal DSLTrans transformation is composed of a sequence of layers where each layer is composed of a set of rules. The last condition of \cref{def:layer_transformation_appendix} imposes that, for any two pair of rules in the transformation, the matcher of the second rule never partially or totally subsumes (or contains) the matcher of the first rule, unless the second rule is in a subsequent layer and produces something more than the first rule. This condition avoids situations where the execution of a rule in a DSLTrans model transformation necessarily implies the execution of another rule (except for when rules having backward links necessarily execute because all their dependencies were created during the execution of previous layers).

@@

%<*pccfrc>
\reviewer{A $\sqcup$ operator is defined in Def. 19, but there you seem to
  rely on the fact that some elements of the path conditions and
  some elements of the rule are identical, otherwise the union
  would not work. Since a rule can be applied in several places,
  this would require a renaming of the rule elements, which - as 
  far as I could see - is not specified.}

@@

where we have that $V=V'\cup V''$, $E'\cup E''\subseteq E$, $st'\cup
st''\subseteq st$, $\tau'\cup \tau''\subseteq \tau$ and if $v_1\xrightarrow{e}
v_2\in E\setminus E'\cup E''$ then we have that $v_1\in Apply(V'')$, $v_1\notin Apply(V')$, $v_2\in Match(V'')$ and also that $\tau'(e)=trace$. Additionally, $Match = Match'\sqcup Match''$ and $Apply = Apply'\sqcup Apply''$. Finally, we have that: $Rulecop = Rulecop'\cup$ {rl}.

@@

Let $tr\in \textsc{Transf}^{sr}_{tg}$ be a DSLTrans transformation. Let also $pc = \langle V,E,st,\tau,Match,Apply,Rules\rangle \in
\textsc{Pathcond}(tr)$ of a path condition of $tr$ and $ex = \langle V',E',st',\tau',Input,Output\rangle \in Exec(tr)$ be an execution of $tr$. We have that $ex$ is abstracted by $pc$, noted $ex\Vvdash pc$, if and only if the set of transformation rules of $tr$ combined in $pc$ and the set of transformation rules of $tr$ used to built $ex$ is the same, and:
\begin{multline}
\label{eq:abstr_input_output}
\big(\forall rl\in Rules\;.\;Match(rl) \vartriangleleft Input^*\big) \;\land\; Output \blacktriangleleft Apply
\end{multline}
\center{and}
\begin{multline}
\label{eq:abstr_trace}
\big(\forall trc\in Components(pc|_{trace})\;.\;trc\vartriangleleft ex\big)\;\land\;\\
\big(\forall e'\in E'\, \exists e\in E\;.\;\tau'(e')=trace \Longrightarrow \tau(e)=trace\big)
\end{multline} 
% where for all $rl,rl'\in Rules$, if $rl\cong rl'$ then there exist two injective typed graph homomorphisms $f$ and $g$ such that $Match(rl)\stackrel{f}{\vartriangleleft} Input^*$, $Match(rl)\stackrel{g}{\vartriangleleft} Input^*$ and $CoDom(f)\neq CoDom(g)$.
% $/pc/ = Apply_{ex}\cup ex|_{trace}$ is the output part of $pc$, including symbolic traceability links.

\reviewer{Definition 28: When you define the abstraction of an execution
  by a path condition, you require two conditions (separated by an
  and). I have the feeling that the morphisms used in both
  conditions should somehow be compatible to each other. However,
  your triangle notation indicates only the existence of a morphisms.
  How do you express that these morphisms somehow "agree"?}
%</abstractionrel>

@@

\reviewer{You can not handle properties with multiple instances of rule 
    element (example in Fig. 25). On p.14 in the answer section,
    you claim that such conditions are excluded in Def. 29. However,
    the last lines of this definition are not easy to understand.
    Please explain why there are there (by giving the explanation
    from the answers section.)

    Without these explanations it is very hard to see why 
    Prop. 3 should hold.}

@@

\reviewer{In Def. 31 I found it confusing that - different from previous
    definitions - the two morphisms now go in the same direction.
    There is an explanation after Definition 31, but I found it 
    very hard to understand.}
Let $tr\in \textsc{Transf}^{sr}_{tg}$ be a transformation. Let also $p = \langle V,E,st,\tau,\\Pre,Post\rangle \in \textsc{Property}(tr)$ be a property of $tr$ and $pc=\big\langle V',E',\\st',\tau', Match,Apply,Rulecop\big\rangle\in \textsc{Pathcond}(tr)$ be a path condition of $tr$. Path condition $pc$ satisfies property $p$, written $pc \vdash p$, if and only if:
\begin{multline*}
\forall f\; \exists g\,.\,\big(in\stackrel{f}{\blacktriangleleft} Pre \implies out \stackrel{g}\blacktriangleleft p\big)\\
\text{where } in \sqsubseteq Match^{*} \;\land\; out \sqsubseteq pc^{*}
\end{multline*}
Additionally $Dom(g)\cap Match(pc^{*}) = Dom(f)$ and $f(v)\neq f(v')$, $g(v)\neq g(v')$ whenever $v$ and $v'$ are elements of the path condition belonging to the same rule copy of set $Rulecop$.

### 2016-05-02 text/property_verification.tex
Add reviewer's comments into the paper.

In order to illustrate this limitation, consider a transformation having one single rule that matches an elements of type A and that produces an element of type X. Our technique will create a path condition as seen in \cref{fig:unprovable_pc}, abstracting over the number of times this rule has executed. According to the definition of satisfaction of a property by a path condition in \cref{def:sat_prop_pc}, the property in \cref{fig:unprovable_prop} does not hold on the path condition in \cref{fig:unprovable_pc}, although intuitively it should.

@@

% As well, we also prove that if a property holds or not on a specific transformation
% execution, it will hold or not on the path condition that represents that
% transformation execution.
\begin{proposition}{(Validity) The result of proving a property on a set of path conditions generated for a transformation or an all executions of that transformation is the same.}
\label{prop:proof_validity}

@@

\begin{proposition}{(Completeness) Properties of a transformation can be shown to either hold for all transformation executions, or not hold for at least one transformation execution.}
\label{prop:proof_completeness}
\end{proposition}
\begin{pf}
This results follows from two previous results: \cref{prop:pc_completeness}, that tells us that every transformation execution is abstracted by one path condition; and \cref{prop:proof_validity} that shows us that every path condition is taken into consideration during property proof. Note that \cref{lem:uniqueness} guarantees consistency of our results, in the sense that the uniqueness of one path condition per transformation execution guarantees that a property cannot be proven to be both \emph{true} and \emph{false} for two path conditions representing the same transformation execution.
\end{pf}

>>>>

In order to illustrate this limitation, consider a transformation having one single rule that matches an element of type A and that produces an element of type X. Our technique will create a path condition as seen in \cref{fig:unprovable_pc}, abstracting over the number of times this rule has executed. According to the definition of satisfaction of a property by a path condition in \cref{def:sat_prop_pc}, the property in \cref{fig:unprovable_prop} does not hold on the path condition in \cref{fig:unprovable_pc}, although intuitively it should.

@@

% As well, we also prove that if a property holds or not on a specific transformation
% execution, it will hold or not on the path condition that represents that
% transformation execution.
\begin{proposition}{(Validity) The result of proving a property on a set of path conditions generated for a transformation or all executions of that transformation is the same.}
\label{prop:proof_validity}

@@

\begin{proposition}{(Completeness) Properties of a transformation can be shown to either hold for all transformation executions, or not hold for at least one transformation execution.}
\label{prop:proof_completeness}
\end{proposition}
\begin{pf}
This result follows from two previous results: \cref{prop:pc_completeness}, that tells us that every transformation execution is abstracted by one path condition; and \cref{prop:proof_validity} that shows us that every path condition is taken into consideration during property proof. Note that \cref{lem:uniqueness} guarantees consistency of our results, in the sense that the uniqueness of one path condition per transformation execution guarantees that a property cannot be proven to be both \emph{true} and \emph{false} for two path conditions representing the same transformation execution.
\end{pf}
